\chapter*{}
%\thispagestyle{empty}
%\cleardoublepage

%\thispagestyle{empty}

\input{portada/portada_2}



\cleardoublepage

\thispagestyle{empty}


\begin{center}
{\large\bfseries Cryptanalysis Ciphertext Based Genetic Algorithms: Breaking Transposition and Substitution Ciphers with Genetic Algorithm}\\
\end{center}
\begin{center}
Abdullah, AL Musawi(student)\\
\end{center}

%\vspace{0.7cm}
\noindent{\textbf{Keywords}: Cryptanalysis, Genetic Algorithm, Transposition Cipher, substitution
cipher, decryption ,optimization search.}\\

\vspace{0.7cm}
\noindent{\textbf{Abstract}}\\

This thesis describes a method of deciphering messages encrypted with transposition cipher and substitution cipher utilising a Genetic Algorithm to search the keyspace.
There are many tools used in the cryptanalysis, Genetic algorithm(GA) is an optimization search tool to find the best solution.

In this project, A fitness measure based on \textbf{English Letter Frequencies} for random of text is described which got it by generating random popultaion. 
The results are compared to those given using a previously published technique and found to be superior.

\chapter*{}
\thispagestyle{empty}

\noindent\rule[-1ex]{\textwidth}{2pt}\\[4.5ex]

Yo, \textbf{Abdullah Taher Saadoon AL Muswai}, alumno de la titulación  máster de Ingeniería Informática  de la \textbf{Escuela Técnica Superior de Ingenierías Informática y de Telecomunicación de la Universidad de Granada}, con DNI A11518169, autorizo la
ubicación de la siguiente copia de mi Trabajo Fin de Master en la biblioteca del centro para que pueda ser
consultada por las personas que lo deseen.

\vspace{6cm}

\noindent Fdo: Abdullah Taher Saadoon AL Muswai

\vspace{2cm}

\begin{flushright}
Granada a 10 de septimpre de 2020.
\end{flushright}


\chapter*{}
\thispagestyle{empty}

\noindent\rule[-1ex]{\textwidth}{2pt}\\[4.5ex]

D. \textbf{ Juan Julián Merelo Guervos (tutor)}, Profesor del Departamento de Arquitectura y Tecnología de Computadores de la Universidad de Granada.

\vspace{0.5cm}



\vspace{0.5cm}

\textbf{Informan:}

\vspace{0.5cm}

Que el presente trabajo, titulado \textit{\textbf{Cryptanalysis Ciphertext Based Genetic Algorithms,Breaking Transposition and Substitution Ciphers with Genetic Algorithm}},
ha sido realizado bajo su supervisión por \textbf{Abdullah Taher Saadoon AL Muswai (alumno)}, y autorizamos la defensa de dicho trabajo ante el tribunal
que corresponda.

\vspace{0.5cm}

Y para que conste, expiden y firman el presente informe en Granada a X de mes de 201 .

\vspace{1cm}

\textbf{Los directores:}

\vspace{5cm}

\noindent \textbf{Juan Julián Merelo Guervos (tutor) \ \ }

\chapter*{Acknowledgements}
\thispagestyle{empty}

       \vspace{1cm}
       After the end of the most difficult and most beautiful journey in my life,
       I want to say that it was so difficult for me that I faced many problems the big one was the Spanish  Language that I could not understand well what the professors were speaking in the classes, But day after day I was able to overcome this problem, Being away from the family for a long time was also one of the most difficult problems, now I can say that I have a very great scientific, social, and cultural experience.\\
First of all, my great thanks to gratitude mighty Allah who helped me to begin this work and finish it successfully.
I would also like to thank \textsf{Dr. Juan Julián Merelo Guervos} who helped and guided me throughout the writing of this TFM. I appreciate his support and the time he granted me to accomplish this work. I am thankful for all of his advice, knowledge, and critical remarks that have helped me improve this work.\\
I would like to take this opportunity to express my gratitude to the information engineering department at the University of Granada , which gave me the required knowledge and spirit to accomplish my Master’s Degree.\\
I would especially like to show my utmost appreciation to my parents, and friends for their generous encouragement, guidance, and invaluable assistance during my study. Dad, Mam and friends, I really appreciate your mentorship and inspiration toward the study of master degree.\\
Spain and its people, I will ever never forget you, Big love and thank you very much


